---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Explode-assignment operators

<!-- badges: start -->
<!-- badges: end -->

This package provides two alternative assignment operators for R:

```

    |             ||
    V             VV
    *             **
 
 explode-       double-
 assign         explode-
                assign

```

Inspired by Matt Dray's "down-assign" operator (see his [tweet](https://twitter.com/mattdray/status/1533996890341183488) and [blog post](https://www.rostrum.blog/2022/06/07/assign-down/)),
the explode-assign and double-explode-assign operators are for when you *really* want to
assign values to variables. 

The main difference between {explodeAssign} and Matt Dray's proposal is 
that {explodeAssign} does not require pre-processing, so all you need to do is
install the package. Like Matt Dray's proposal, it is also a terrible idea.

## Installation

You can install the development version of {explodeAssign} like so:

``` r
remotes::install_github("mjskay/explodeAssign")
```

This is definitely never going to be on CRAN ;).

## Examples

```{r setup, message=FALSE}
library(explodeAssign)
```

The explode-assignment operator is useful when you emphatically want to assign
a value to a variable by dropping the value into the variable like a tiny bomb:

```{r}
# note we need parens. that's okay, safety is important!
(
  1
  |
  V
  *
  x
)
```

`x` now contains the value `1`:

```{r}
x
```

Of course, sometimes we really *really* want to assign a value to a variable, no matter where
it's hiding (a la `<<-`). Thus the double-explode-assignment operator:

```{r}
y = 1

f = function() {
  (
    y + 1
    ||
    VV
    **
    y
  )
}

f()
f()
f()
```

## Note

{explodeAssign} is not responsible for any mishaps caused by operator precedence,
stray parens, consummate Vs, or overloaded base operators. Explode-assign at your own risk.
